\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2017-01-12 report/paper.tex
Deleted a word

    % Look up table for kernel values
    According to Bender et al.~\cite{bender} the kernel values could easily be precomputed and used together with a look up-table in order to speed up the calculations. This will result in a 30 $\%$ faster application.  This could ether be done once when the iteration loop begins and the positions for the particles are determined. Another approach would be to compute a discrete representation of the kernel function before the iteration loop and interpolate between to kernel values in the simulation loop in order to find a kernel value for a specific particle.

>>>>

    % Look up table for kernel values
    According to Bender et al.~\cite{bender} the kernel values could easily be precomputed and used together with a look up-table in order to speed up the calculations. This will result in a $30\%$ faster application.  This could be done once when the iteration loop begins and the positions for the particles are determined. Another approach would be to compute a discrete representation of the kernel function before the iteration loop and interpolate between to kernel values in the simulation loop in order to find a kernel value for a specific particle.
